\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    	% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}

%SetFonts

%SetFonts


\title{Knowledge Checks for Chapters 06 -- 09}
\author{DS598 B1 -- DL4DS}
\date{Spring, 2024}							% Activate to display a given date or no date

\begin{document}
%\vspace*{-20pt}
\maketitle

\textit{We also suggest you attempt and review the exercises with solutions provided
on the UDL website, to help strengthen your understanding. No need to turn 
those in however.}

\textit{The \LaTeX \hspace{1pt} format of this assignment is available on the course website.}

\section*{Chapter 06}

\textbf{Problem 6.10} Show that the momentum term \(\mathbf{m}_t\) (equation 6.11) is an
infinite weighted sum of the gradients at the previous iterations and derive an
expression for the coefficients (weights) of that sum.

\textit{Hint:} Write the equation for \(\mathbf{m}_1\) in terms of \(\mathbf{m}_0\)
and then \(\mathbf{m}_2\) in terms of \(\mathbf{m}_1\). Then substitute 
\(\mathbf{m}_1\) for the equation for \(\mathbf{m}_1\) and so on. Look for a 
pattern that you can express compactly.

\section*{Chapter 07}

\textbf{Problem 7.3} What size are each of the terms in equation 7.19? Express
you answer for each term as \( \mathbb{R}^{D_i \times D_j} \), where you replace
\(i\) and \(j\) with the appropriate numbers.

\section*{Chapter 08} 

\textbf{Problem 8.2} What values should we choose for the three weights and
biases in the first layer of the model in figure 8.4a so that the responses at
the hidden units are as depicted in figures 8.4b-d?

\section*{Chapter 09}

\textbf{Problem 9.1} Consider a model where the prior distribution over the
parameters is a normal distribution with mean zero and variance
\(\sigma^2_\phi\) so that
\[Pr(\phi) = \prod_{j=1}^{J} Norm_{\phi_j}[0, \sigma^2_\phi].\]
where \(j\) indexes the model parameters. When we apply a prior, we maximize
\[\prod_{i=1}^{I} Pr(\mathbf{y}_i|\mathbf{x}_i, \phi) Pr(\phi).\] 
Show that the associated loss function of this model is equivalent to \(L_2\) 
regularization.

\textit{Hint:} Calculate the negative log likelihood of the above function and 
then substitute the equation for the prior distribution and simplify.


\end{document}  