\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    	% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}

%SetFonts

%SetFonts


\title{Knowledge Check 5 -- Loss Functions}
\author{DS598 B1 -- DL4DS}
\date{Spring, 2024}							% Activate to display a given date or no date

\begin{document}
%\vspace*{-20pt}
\maketitle

\textbf{Problem 5.2} The loss \(L\) for binary classification for a single
training pair \({x, y}\) is:
\[L = -(1 - y) \log [1 - \mathrm{sig}[f[x,\phi]]] - y \log [sig[f[x,\phi]]] ,\]
where \(sig[\bullet]\) is defined in equation 5.18. Plot this loss as a function
of the transformed network output \(sig[f[x,\phi]] \in [0, 1]\) 
(i) when the training label \(y = 0\) and (ii) when \(y = 1\).

\vspace{1cm}

\textbf{Problem 5.3} \textit{Optional problem, but recommend doing it. Hint: you
should be able to answer in 3-4 lines of math. You don't have define what the
Bessel function is. Just leave it as a symbol.}

\vspace{1cm}

\textbf{Problem 5.6} Consider building a model to predict the number of
pedestrians \(y \in {0, 1, 2, . . .}\)
that will pass a given point in the city in the next minute, based on data \(x\)
that contains information about the time of day, the longitude and latitude, and
the type of neighborhood. A suitable distribution for modeling counts is the
Poisson distribution (figure 5.15 from book). This has a single parameter
\(\lambda > 0\) called the rate that represents the mean of the distribution.
The distribution has probability density function:
\[Pr(y = k) = \frac{\lambda^k e^{-\lambda}}{ k!}. \]
Use the recipe in section 5.2 to design a loss function for this model assuming
that we have access to \(I\) training pairs \(\{xi, yi\}\).

\vspace{1cm}

\textbf{Problem 5.7} Consider a multivariate regression problem where we predict
10 outputs so \(\mathbf{y} \in R^{10}\) and model each with an independent normal
distribution where the means \(\mu_d\) are predicted
by the network, and variances \(\sigma^2\) are all the same. Write an expression
for the likelihood \(Pr(\mathbf{y}|\mathbf{f}[\mathbf{x},\phi])\) for this
model. Show that minimizing the
negative log-likelihood of this model is still equivalent to minimizing a sum of
squared terms if we don't estimate the variance \(\sigma^2\).

\end{document}  